Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-08-15 paper/ms.tex
word treak and add JMB affil

\author[0000-0002-9873-1471]{John M. Brewer}
\affil{Department of Astronomy, Yale University, 260 Whitney Ave,
  New Haven, CT 06511, USA}

@@

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk}),
are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
The statistical uncertainties for each parameter
presented in \tablename~\ref{tab:kk} from \citealt{2016ApJS..225...32B}
are estimated from repeated measurements of multiple spectra of the same stars.
We note that while there may be systematic uncertainties (bias) in the elemental
abundances of these two stars unconstrained by this procedure,
the systematic uncertainties for these two solar-type ``twin-like'' stars in
terms of $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
the observed abundance differences.

%TODO: plot styles...
\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
    Sun (grey).
    For \sunanalog, the initial conditions are set to the median of the
    posterior samples over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala} (\citealt{gala}).
    Right panel: distribution of maximum $z$-heights for orbits computed from
    all posterior samples.
  }
  \label{fig:orbit}
\end{figure}

>>>>

\author[0000-0002-9873-1471]{John M. Brewer}
\affil{Department of Astronomy, Yale University, 260 Whitney Ave,
  New Haven, CT 06511, USA}
\affil{Department of Astronomy, Columbia University, 550 West 120th Street,
  New York, NY 10027, USA}

@@

We stress that none of the other four twin-like ($\Delta T_\mathrm{eff}
\lesssim 100$~K) wide binary pairs examined by \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
As shown in \figname~\ref{fig:deltaXH},
the differences in other pairs for all elements except \elem{N} and \elem{O},
which are also the most uncertain (\tablename~\ref{tab:kk}),
are less than $0.05$~dex, making \bizarreone-\sunanalog\ pair a significant outlier.
The statistical uncertainties for each parameter
presented in \tablename~\ref{tab:kk} from \citealt{2016ApJS..225...32B}
are estimated from repeated measurements of multiple spectra of the same stars.
We note that while there may be systematic uncertainties (bias) in the elemental
abundances of these two stars unconstrained by this procedure,
the systematic uncertainties for these two solar-type ``twin-like'' stars
with small differences in $T_\mathrm{eff}$ and $\log{g}$, if any, are unlikely to wash out
the observed abundance differences of $\approx 0.2$~dex.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
    Sun (grey).
    For \sunanalog, the initial conditions are set to the median of the
    posterior samples over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala} (\citealt{gala}).
    Right panel: distribution of maximum $z$-heights for orbits computed from
    all posterior samples.
  }
  \label{fig:orbit}
\end{figure}
